\documentclass{sigchi}

% Use this command to override the default ACM copyright statement (e.g. for preprints). 
% Consult the conference website for the camera-ready copyright statement.


% EXAMPLE BEGIN -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)
 \toappear{Permission to make digital or hard copies of all or part of this work for personal or classroom use is granted without fee provided that copies are not made or distributed for profit or commercial advantage and that copies bear this notice and the full citation on the first page. Copyrights for components of this work owned by others than ACM must be honored. Abstracting with credit is permitted. To copy otherwise, or republish, to post on servers or to redistribute to lists, requires prior specific permission and/or a fee. Request permissions from permissions@acm.org. \\
 {\emph{CHI'14}}, April 26--May 1, 2014, Toronto, Canada. \\
 Copyright \copyright~2014 ACM ISBN/14/04...\$15.00. \\
 DOI string from ACM form confirmation}
% EXAMPLE END -- HOW TO OVERRIDE THE DEFAULT COPYRIGHT STRIP -- (July 22, 2013 - Paul Baumann)


% Arabic page numbers for submission. 
% Remove this line to eliminate page numbers for the camera ready copy
\pagenumbering{arabic}


% Load basic packages
\usepackage{balance}  % to better equalize the last page
\usepackage{graphics} % for EPS, load graphicx instead
\usepackage{times}    % comment if you want LaTeX's default font
\usepackage{url}      % llt: nicely formatted URLs

% llt: Define a global style for URLs, rather that the default one
\makeatletter
\def\url@leostyle{%
  \@ifundefined{selectfont}{\def\UrlFont{\sf}}{\def\UrlFont{\small\bf\ttfamily}}}
\makeatother
\urlstyle{leo}


% To make various LaTeX processors do the right thing with page size.
\def\pprw{8.5in}
\def\pprh{11in}
\special{papersize=\pprw,\pprh}
\setlength{\paperwidth}{\pprw}
\setlength{\paperheight}{\pprh}
\setlength{\pdfpagewidth}{\pprw}
\setlength{\pdfpageheight}{\pprh}

% Make sure hyperref comes last of your loaded packages, 
% to give it a fighting chance of not being over-written, 
% since its job is to redefine many LaTeX commands.
\usepackage[pdftex]{hyperref}
\hypersetup{
pdftitle={SIGCHI Conference Proceedings Format},
pdfauthor={LaTeX},
pdfkeywords={SIGCHI, proceedings, archival format},
bookmarksnumbered,
pdfstartview={FitH},
colorlinks,
citecolor=black,
filecolor=black,
linkcolor=black,
urlcolor=black,
breaklinks=true,
}

% create a shortcut to typeset table headings
\newcommand\tabhead[1]{\small\textbf{#1}}


% End of preamble. Here it comes the document.
\begin{document}

\title{MindMargin: Capturing Reader Engagement with an Article-Adjacent Commenting Platform}

\numberofauthors{3}
\author{
  \alignauthor Daniel Haehn\\
    \affaddr{Harvard University}\\
    \affaddr{Cambridge, MA, USA}\\
    \email{haehn@seas.harvard.edu}\\
    \affaddr{}
  \alignauthor Sharon Zhou\\
    \affaddr{Harvard University}\\
    \affaddr{Cambridge, MA, USA}\\
    \email{zhou12@college.harvard.edu}\\
    \affaddr{}    
  \alignauthor 3rd Author Name\\
    \affaddr{Affiliation}\\
    \affaddr{Address}\\
    \email{e-mail address}\\
    \affaddr{Optional phone number}
}

\maketitle

\begin{abstract}
Commenting systems are popular throughout many websites. Reading and writing comments can support passive consumption of media by increasing active user engagement in many ways. Information exchange, personal reflection, and lively discussion are only some possible outcomes. We explore how user engagement can be increased by proposing a new commenting system and interface, MindMargin. In contrast to traditional commenting systems where comments are featured below the article, MindMargin presents comments adjacent to its reference media. Users can post and navigate comments and replies on a horizontal infinite scroll. This exposes users to a diverse array of opinions as they read since comments in our system are anchored to relevant areas of the article. 

Furthermore, we propose a novel metric for classifying and more visibly displaying "popular" comments. Our metric includes the number of up- and down-votes as well as the post time. This guarantees that new comments are visible even if many popular comments already populate the article.

We define three hypotheses to measure increased user engagement that A) investigate if article-adjacent comments generate more comments, B) explore if permanent exposure to comments while reading impacts individual stance towards an issue or opinion in the article, and C) measure the influence of article-adjacent comments on a reader's impression of the comments. From a user study with 46 young adults, we accepted the second and third hypotheses. We explain the rejection of the first hypothesis as a result of various factors, including the novelty effect. We also discuss how the rejection of our first hypothesis coupled with acceptance of our second and third, in fact, further support our conclusions on increased reader engagement in MindMargin.

Based on our initial evaluation and results, we have concluded that the proposed MindMargin system is superior to traditional commenting systems in increasing user engagement while reading articles.
\end{abstract}

\keywords{
	Comments; commenting system; anchored; user engagement.
}

%\category{H.5.2.}{Information Interfaces and Presentation (e.g. HCI)}{User Interfaces}

\input{introduction.tex}

\input{relatedwork.tex} 

\input{technology.tex}

\input{experiment.tex}

\input{results_and_discussion.tex}

\input{conclusion.tex}

\bibliographystyle{acm-sigchi}
\bibliography{lit}
\end{document}
